% ICCV 2025 Paper Template; see https://github.com/cvpr-org/author-kit

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
\usepackage{iccv}              % To produce the CAMERA-READY version
%\usepackage[review]{iccv}      % To produce the REVIEW version
% \usepackage[pagenumbers]{iccv} % To force page numbers, e.g. for an arXiv version

% Import additional packages in the preamble file, before hyperref
\input{preamble}
\usepackage{amssymb}
\usepackage{pifont}

% --- Required Packages ---
\usepackage{tikz}           % For drawing diagrams
\usepackage{pgfplots}       % For plotting graphs


% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, 
% e.g. with the file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete *.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you should be clear).
\definecolor{iccvblue}{rgb}{0.21,0.49,0.74}
\usepackage[pagebackref,breaklinks,colorlinks,allcolors=iccvblue]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\paperID{28} % *** Enter the Paper ID here
\def\confName{ICCV}
\def\confYear{2025}

%%%%%%%%% TITLE - PLEASE UPDATE
%\title{Retaining Knowledge in Continual VQA Without Visual Memory: A Question-Reply Approach}

\title{Ask and Remember: A Questions-Only Replay Strategy for Continual Visual Question Answering}
%\title{No Images, No Problem: Retaining Knowledge in Continual VQA with Questions-Only Memory}

% QUAD: Efficient Functional Regularization for Continual VQA without Visual Memory
%%%%%%%%% AUTHORS - PLEASE UPDATE
% \author{First Author\\
% Institution1\\
% Institution1 address\\
% {\tt\small firstauthor@i1.org}
% % For a paper whose authors are all at the same institution,
% % omit the following lines up until the closing ``}''.
% % Additional authors and addresses can be added with ``\and'',
% % just like the second author.
% % To save space, use either the email address or home page, not both
% \and
% Second Author\\
% Institution2\\
% First line of institution2 address\\
% {\tt\small secondauthor@i2.org}
% }

\author{
Imad Eddine Marouf$^{1}$
\and
Enzo Tartaglione$^{1}$
\and 
Stéphane Lathuilière$^{1,2}$
\and 
Joost van de Weijer$^{3}$ \\
{\tt\small $^{1}$ LTCI, Télécom-Paris, Institut Polytechnique de Paris, France}\\{\tt\small $^{2}$Inria, LJK,  Univ.~Grenoble Alpes, France, $^{3}$Universitat Autónoma de Barcelona, Spain} %\\
%{\tt\small $^{1}$first.lastname@telecom-paris.fr, $^{2}$stephane.lathuiliere@inria.fr, $^{3}$joost@cvc.uab.es}
}




% \institute{$^{1}$Télécom-Paris, Institut Polytechnique de Paris, $^{2}$University of Aberdeen\\
% \email{$^{1}$\{first.lastname\}@telecom-paris.fr}
% }

\begin{document}
\maketitle
\input{sec/abstract}    
\input{sec/intro}
\input{sec/related}
\input{sec/method}
\input{sec/experiments}
\section{Conclusion}
\label{sec:conclusion}
In this work, we introduced \textsc{\textbf{QU}estion-only replay with \textbf{A}ttention \textbf{D}istillation} (\qstmethodshort{}), a novel questions-only replay framework for continual VQA. Unlike conventional methods that store both images and questions, \qstmethodshort{} addresses storage and privacy concerns by retaining only past task questions. This design enables effective regularization without storing sensitive visual data, making it highly practical for privacy-conscious applications. Comprehensive evaluations on VQAv2 and NExT-QA show that \qstmethodshort{} consistently outperforms both memory-free and memory-rehearsal methods, achieving state-of-the-art performance.  Surprisingly, our method, without any image exemplars, outperforms previous methods, which do require image storage. \\
\textbf{Acknowledgements. }This paper is supported by the French National Research Agency (ANR) in the framework of the JCJC project “BANERA under Grant ANR-24-CE23-4369, and was funded by the European Union's Horizon Europe research and innovation program under grant agreement No. 101120237 (ELIAS). It was also partially funded by Hi!PARIS Center on Data Analytics and Artificial Intelligence and was granted access to the HPC resources of IDRIS under the allocation AD011013860 made by GENCI.
{
    \small
    \bibliographystyle{ieeenat_fullname}
    \bibliography{main}
}
% WARNING: do not forget to delete the supplementary pages from your submission 
\input{sec/X_suppl}

\end{document}
