%
% File emnlp2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith
%\listfiles
\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

\usepackage{graphicx}
\usepackage[export]{adjustbox}
\usepackage{url}
\usepackage{bm}
\usepackage{here}
%\usepackage[fleqn]{amsmath}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{enumitem}

\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{soul}
\usepackage{float}
\usepackage{subfigure}
% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\newcommand{\argmax}[1]{\underset{#1}{\operatorname{arg}\,\operatorname{max}}\;}

\title{Discriminative Nearest Neighbor Few-Shot Intent Detection\\ by Transferring Natural Language Inference}

\author{
  \textbf{Jian-Guo Zhang}$^1$\thanks{\ \ Work done while the first author was an intern at Salesforce Research.}~~~~ \textbf{Kazuma Hashimoto}$^2$\thanks{\ \ Corresponding author.}~~~~ \textbf{Wenhao Liu}$^2$~~~~ \textbf{Chien-Sheng Wu}$^2$~~~~  \\ \textbf{Yao Wan}$^3$~~~~ \textbf{Philip S. Yu}$^1$~~~~  \textbf{Richard Socher}$^2$~~~~ \textbf{Caiming Xiong}$^2$ \\
  $^1$ University of Illinois at Chicago, Chicago, USA \\
  $^2$Salesforce Research,  Palo Alto, USA \\
  $^3$Huazhong University of Science and Technology, Wuhan, China\\
  { \texttt{\{jzhan51,psyu\}@uic.edu}, \texttt{wanyao@hust.edu.cn} } \\
  { \texttt{\{{k.hashimoto,wenhao.liu,wu.jason,rsocher,cxiong\}@salesforce.com}} }
}


\date{}

\begin{document}
\maketitle
\begin{abstract}
% Intent detection is crucial in goal-oriented dialog to identify whether each user utterance has an intent or not.
% Intent candidates are different across different systems, and few-shot learning attracts our interest to instantly build a new system.
% This paper presents a simple yet effective approach to robust and accurate example-based intent detection.
% Unlike previous studies on few-shot intent classification, we focus on the task along with out-of-scope detection.

% Jason rewrote, feel free to change it back
%We also equip our system with the ability to detect an out-of-scope intent when the intent is supposed to be a novel intent.

% Intent detection is one of the core components of goal-oriented dialog systems in practice. 
%However, pre-defining and collecting data for all the possible intents are hard and costly due to the unconstrained user behavior and growing domains.
% In this paper, we focus on few-shot intent detection and present a simple yet effective approach to discriminative example-based classification.

Intent detection is one of the core components of goal-oriented dialog systems, and detecting out-of-scope (OOS) intents is also a practically important skill.
Few-shot learning is attracting much attention to mitigate data scarcity, but OOS detection becomes even more challenging.
In this paper, we present a simple yet effective approach, discriminative nearest neighbor classification with deep self-attention.
Unlike softmax classifiers, we leverage BERT-style pairwise encoding to train a binary classifier that estimates the best matched training example for a user input.
We propose to boost the discriminative ability by transferring a natural language inference (NLI) model.
Our extensive experiments on a large-scale multi-domain intent detection task show that our method achieves more stable and accurate in-domain and OOS detection accuracy than RoBERTa-based classifiers and embedding-based nearest neighbor approaches.
More notably, the NLI transfer enables our 10-shot model to perform competitively with 50-shot or even full-shot classifiers, while we can keep the inference time constant by leveraging a faster embedding retrieval model. 

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{introduction.tex}
\input{methodology.tex}
\input{settings.tex}
\input{experiments.tex}
% %\input{discussion.tex}
\input{related-work.tex}
\input{conclusion.tex}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgments}
This work is supported in part by NSF under grants III-1763325, III-1909323, and SaTC-1930941.
We thank Huan Wang, Wenpeng Yin for their insightful discussions, and the anonymous reviewers for their helpful and thoughtful comments.
We also thank Jin Qu, Tian Xie, Xinyi Yang, and Yingbo Zhou for their support in the deployment of DNNC into the internal system.

% remove this later!!
%\clearpage

\bibliographystyle{acl_natbib}
\bibliography{emnlp2020}

%\clearpage
\input{supplementary.tex}

%\clearpage

\end{document}
