\section{Discussions and Related Work}
% NEED MORE

\paragraph{Interpretability}
Interpretability is an important line of research recently~\citep{interpret-qa-1,interpret-qa-2,graph-retriever}.
The nearest neighbor approach~\citep{knn-nips} is appealing in that we can explicitly know which training example triggers each prediction.
Table~\ref{table:case-study} in Appendix~\ref{extra-results} shows some examples.

\paragraph{Call for better embeddings}
Emb-$k$NN and RN-$k$NN are not as competitive as DNNC.
This encourages future work on the task-oriented evaluation of text embeddings in $k$NN.

\paragraph{Training time}
Our DNNC method needs longer training time than that of the classifier (e.g., 90 vs. 40 seconds to train a single-domain model), because we synthesize the pairwise examples.
As a first step, we used all the training examples to investigate the effectiveness, but it is an interesting direction to seek more efficient pairwise training.

\paragraph{Distilled model}
Another way to speedup our model is to use distilled pre-trained models~\citep{distil-bert}.
We replaced the RoBERTa model with a distilled RoBERTa model,
%\footnote{\url{https://s3.amazonaws.com/models.huggingface.co/bert/distilroberta-base-config.json}.}
and observed large variances with significantly lower OOS accuracy.
\citet{acl-ood} also suggested that the distilled models would not be robust to out-of-distribution examples.

% will be revised later
\paragraph{Few-shot text classification}
%Few-shot classification~\cite{fei2006one,vinyals2016matching} learns classifiers given only a few labeled examples of each class.
%In NLP applications, it has been used for semantic parsing~\cite{N18-2115}, machine translation ~\cite{D18-1398}, text classification~\cite{deng2019low,geng2019induction,xu2019open}, dialogue state tracking~\cite{wu-etal-2019-transferable}, and intent classification~\citep{marrying-reg,efficient_intent} without OOS.
% These tasks usually employ multiple domains to achieve fast adaptation, while in our case the number of existing domains is limited.
Few-shot classification~\citep{fei2006one,vinyals2016matching} has been applied to text classification tasks~\citep{deng2019low,geng2019induction,xu2019open}, and few-shot intent detection is also studied but without OOS~\citep{marrying-reg,xia2020cg,efficient_intent}.
There are two common scenarios: 1) learning with plenty of examples and then generalizing to unseen classes with a few examples, and 2) learning with a few examples for all seen classes.
Meta-learning~\citep{finn2017model,geng2019induction} is widely studied in the first scenario.
%, using large labeled meta-train and meta-test data to optimize model parameters with second-order gradients.
In our paper, we have focused on the second scenario, assuming that there are only a limited number of training examples for each class.
Our work is related to metric-based approaches such as matching networks~\cite{matching-net}, prototypical networks~\cite{proto-net} and relation networks~\cite{relation_net}, as they model nearest neighbours in an example-embedding or a class-embedding space.
%and kernel density estimation.
We showed that a relation network with the RoBERTa embeddings does not perform comparably to our method.
We also considered several ideas from prototypical networks~\citep{hierarchical-proto-net}, but those did not outperform our Emb-$k$NN baseline.
These results indicate that deep self-attention is the key to the nearest neighbor approach with OOS detection.

% General approaches usually fall into two categories: optimization-based approaches and metric-based approaches.
% Optimization-based approaches such as meta-learning frameworks~\cite{finn2017model,geng2019induction} use large labeled meta-train and meta-test data to optimize model parameters with second-order gradients and learn to fast adapt to the few-shot examples during inference. 
% learn to extract transferable knowledge from a large labeled training set with a set of seen classes, and optimize model parameters based on gradients computed from the few-shot examples.
% In our paper, we focus on the second scenario, assuming there are only a limited number of training examples for each class. 
% Metric-based approaches such as Match Networks~\cite{matching-net}, Prototypical Networks~\cite{proto-net} and Relation Networks~\cite{relation_net} are similar to nearest neighbours and kernel density estimation.
% Recently, some approaches are also proposed for few-shot text classification~\cite{deng2019low,geng2019induction,xu2019open} and few-shot intent classification~\citep{marrying-reg,efficient_intent} without OOS.